Comb associative operads

### 2018-07-20 CAs_operads.tex
Modifications après relecture des deux premières sections

\begin{Lemma} \label{lem:first_dimensions_CAs}
    For any positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
    and $n \leq \gamma + 1$,
    \begin{equation}
        \# \CAs{\gamma}(n) =
        \begin{cases}
            \Catalan(n)
                & \mbox{ if } n \leq \gamma, \\
            \Catalan(\gamma + 1) - 1
                & \mbox{ otherwise } (n = \gamma + 1).
        \end{cases}
    \end{equation}
\end{Lemma}
\begin{proof}
    Since the equivalence relation $\CongrCAs{\gamma}$ is trivial on the
    binary trees of degrees $d < \gamma$, and since a binary tree of
    degree $d$ has arity $n := d + 1$, one has
    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with $n \leq \gamma$.
    Besides, by definition of $\CongrCAs{\gamma}$, all the
    $\CongrCAs{\gamma}$-equivalence classes of binary trees of degree
    $\gamma$ are trivial, except one consisting in the pair
    $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
    binary tree of degree $d$ has arity $n := \gamma + 1$,
    \begin{math}
        \# \CAs{\gamma}(n)
        = \# \Mag(\gamma + 1) - 1
        = \Catalan(\gamma + 1) - 1.
    \end{math}
\end{proof}
\medbreak

@@

\begin{Theorem}\label{thm:lattice_CAs}
  The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
  defined, for any positive integers $\gamma$ and $\gamma'$, by
    \begin{equation}
      \CAs{\gamma}\InfCAs\CAs{\gamma'}
      =\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
    \end{equation}
    and
    \begin{equation}
      \CAs{\gamma}\SupCAs\CAs{\gamma'}
      =\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}
\medbreak

\begin{Remark}
  The lattice $\left(\N,\mid, \gcd, \lcm\right)$ admits $1$ as minimum
  element and $0$ as maximum element: any nonnegative integer is
  divisible by $1$ and divides $0$. The corresponding property for
  $\LatCAs$ is that it admits $\As=\CAs{2}$ as minimum element and $\Mag=
  \CAs{1}$ as maximum element: any comb associative operad projects onto
  $\As$ and is a quotient of $\Mag$.
\end{Remark}

@@

\begin{Theorem}
    The inclusion
    \begin{math}
        \iota:\left(\KCAsAll,\OrdCAs\right)
        \to
        \left(\QMag,\OrdQMag\right)
    \end{math}
    is nondecreasing. In particular, for any positive integers $\gamma$
    and $\gamma'$, we have
    \begin{equation} \label{equ:comparison_of_lattice_operations}
        \KCAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
        \OrdQMag
        \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
    \end{equation}
    and
    \begin{equation}
        \KCAs{\gamma}\SupQMag\KCAs{\gamma'}
        \OrdQMag
        \KCAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}

\begin{Remark}
  Note that $\LatKCAs$ does not embed into a sub-lattice of $\LatQMag$,
  that is $\iota$ is not a lattice morphism. Consider for instance
  $\gamma=3$ and $\gamma'=4$, then $\KCAs{\gamma}\InfCAs\KCAs{\gamma'}$
  is equal to $\KCAs{2}=\K\As$, whereas
  $\KCAs{\gamma}\InfQMag\KCAs{\gamma'}$ is quotient of $\KMag$ be the two
  relations $\LComb{3}-\RComb{3}$ and $\LComb{4}-\RComb{4}$.
\end{Remark}

>>>>

\begin{Lemma} \label{lem:first_dimensions_CAs}
    For all positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
    and $n \leq \gamma + 1$,
    \begin{equation}
        \# \CAs{\gamma}(n) =
        \begin{cases}
            \Catalan(n)
                & \mbox{ if } n \leq \gamma, \\
            \Catalan(\gamma + 1) - 1
                & \mbox{ otherwise } (n = \gamma + 1).
        \end{cases}
    \end{equation}
\end{Lemma}
\begin{proof}
    Since the equivalence relation $\CongrCAs{\gamma}$ is trivial on the
    binary trees of degrees $d < \gamma$, and since a binary tree of
    degree $d$ has arity $n := d + 1$, one has
    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with $n \leq \gamma$.
    Besides, by definition of $\CongrCAs{\gamma}$, all the
    $\CongrCAs{\gamma}$-equivalence classes of binary trees of degree
    $\gamma$ are trivial, except one consisting in the pair
    $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
    binary tree of degree $d$ has arity $n := \gamma + 1$,
    \begin{math}
        \# \CAs{\gamma}(n)
        = \# \Mag(\gamma + 1) - 1
        = \Catalan(\gamma + 1) - 1.
    \end{math}
\end{proof}
\medbreak

@@

\begin{Theorem}\label{thm:lattice_CAs}
  The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
  defined, for all positive integers $\gamma$ and $\gamma'$, by
    \begin{equation}
      \CAs{\gamma}\InfCAs\CAs{\gamma'}
      =\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
    \end{equation}
    and
    \begin{equation}
      \CAs{\gamma}\SupCAs\CAs{\gamma'}
      =\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}
\medbreak

  The lattice $\left(\N,\mid, \gcd, \lcm\right)$ admits $1$ as minimum
  element and $0$ as maximum element: any nonnegative integer is
  divisible by $1$ and divides $0$. The corresponding property for
  $\LatCAs$ is that it admits $\As=\CAs{2}$ as minimum element and $\Mag=
  \CAs{1}$ as maximum element: any comb associative operad projects onto
  $\As$ and is a quotient of $\Mag$.

@@

\begin{Theorem}
    The inclusion
    \begin{math}
        \iota:\left(\KCAsAll,\OrdCAs\right)
        \to
        \left(\QMag,\OrdQMag\right)
    \end{math}
    is nondecreasing. In particular, for all positive integers $\gamma$
    and $\gamma'$, we have
    \begin{equation} \label{equ:comparison_of_lattice_operations}
        \KCAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
        \OrdQMag
        \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
    \end{equation}
    and
    \begin{equation}
        \KCAs{\gamma}\SupQMag\KCAs{\gamma'}
        \OrdQMag
        \KCAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}

  Note that $\LatKCAs$ does not embed into a sub-lattice of $\LatQMag$,
  that is $\iota$ is not a lattice morphism. Consider for instance
  $\gamma=3$ and $\gamma'=4$, then $\KCAs{\gamma}\InfCAs\KCAs{\gamma'}$
  is equal to $\KCAs{2}=\K\As$, whereas
  $\KCAs{\gamma}\InfQMag\KCAs{\gamma'}$ is quotient of $\KMag$ be the two
  relations $\LComb{3}-\RComb{3}$ and $\LComb{4}-\RComb{4}$.

### 2018-07-20 Magmatic_operads.tex
Modifications après relecture des deux premières sections

We denote by $\IMag$ the set of operadic ideals of $\KMag$, and we set
\begin{equation} \label{equ:definition_of_QMag}
    \QMag := \Big\{\KMag/_I :  I\in\IMag\Big\},
\end{equation}
as the set of the quotients of the linear magmatic operad. Given
$\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
$I$-equivalence of $x$. Observe that $\KMag/_I$ is generated as an
operad by $[\Product]_I$. Moreover, given two  elements $\Oca_1$ and
$\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
set of operad morphism from $\Oca_1$ to~$\Oca_2$.
\medbreak

@@

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
    The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
    The map $\mathcal{Q}:\IMag\to\QMag$ defined by
    $\mathcal{Q}(I) := \KMag/_I$ is a bijection by definition of
    $\QMag$. Moreover, from
    Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
    $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
    $\left(\QMag,\OrdQMag\right)$ is a poset and $\mathcal{Q}$ is a
    decreasing bijection. The tuple
    $\left(\IMag,\subseteq,\cap,+\right)$ being a lattice, the
    decreasing bijection $\mathcal{Q}$ induces lattice operations on
    $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
\end{proof}
\medbreak

>>>>

We denote by $\IMag$ the set of operadic ideals of $\KMag$, and we set
\begin{equation} \label{equ:definition_of_QMag}
    \QMag := \Big\{\KMag/_I :  I\in\IMag\Big\},
\end{equation}
as the set of the quotients of the linear magmatic operad. Given
$\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
$I$-equivalence of $x$. Observe that $\KMag/_I$ is generated as an
operad by $[\Product]_I$. Moreover, given two  elements $\Oca_1$ and
$\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
set of linear operad morphism from $\Oca_1$ to~$\Oca_2$.
\medbreak

@@

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
    The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
  The map $\Oca:\IMag\to\QMag$ defined by $\Oca(I) := \KMag/_I$ is a
  bijection by definition of $\QMag$. Moreover, from
    Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
    $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
    $\left(\QMag,\OrdQMag\right)$ is a poset and $\Oca$ is a decreasing
    bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
    lattice, the decreasing bijection $\mathcal{Q}$ induces lattice
    operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
    definition.
\end{proof}
\medbreak

### 2018-07-20 Operads_rewrite.tex
Modifications après relecture des deux premières sections

When for any binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
$\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$, there
exists a binary tree $\Tfr'$ such that $\Sfr_1 \RewContextRT \Tfr'$ and
$\Sfr_2 \RewContextRT \Tfr'$, we say that $\RewContext$ is
\Def{confluent}. Besides, a tree $\Tfr$ is a \Def{branching tree} for
$\RewContext$ if there exists two different trees $\Sfr_1$ and $\Sfr_2$
satisfying $\Tfr \RewContext \Sfr_1$ and $\Tfr \RewContext \Sfr_2$. In
this case, the pair $\{\Sfr_1, \Sfr_2\}$ is a \Def{branching pair} for
$\Tfr$. Moreover, the branching pair $\{\Sfr_1, \Sfr_2\}$ is
\Def{joinable} if there exists a binary tree $\Tfr'$ such that
$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$. The
diamond lemma~\cite{New42} is based upon the inspection of the branching
pairs of a terminating rewrite relation $\RewContext$ in order to prove
its confluence.
\medbreak

@@

    \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
    with the minimal degree and which is minimal with respect to the
    order $\leq$. Remove $\Tfr$ from $\BranchingTrees$.
    \smallbreak

    \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
    that $\Sfr_1$ and $\Sfr_2$ are minimal with respect to the
    order $\leq$.
    \smallbreak

    \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be two
    different normal forms of $\Sfr_1$ and $\Sfr_2$, respectively.
    \smallbreak

    \item \label{item:new_rewrite_rule_buchberger}
    Add to $\Rew'$ the rewrite rule
    \begin{math}
        \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
        \Rew'
        \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
    \end{math}
    \smallbreak

>>>>

When for all binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
$\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$, there
exists a binary tree $\Tfr'$ such that $\Sfr_1 \RewContextRT \Tfr'$ and
$\Sfr_2 \RewContextRT \Tfr'$, we say that $\RewContext$ is
\Def{confluent}. Besides, a tree $\Tfr$ is a \Def{branching tree} for
$\RewContext$ if there exists two different trees $\Sfr_1$ and $\Sfr_2$
satisfying $\Tfr \RewContext \Sfr_1$ and $\Tfr \RewContext \Sfr_2$. In
this case, the pair $\{\Sfr_1, \Sfr_2\}$ is a \Def{branching pair} for
$\Tfr$. Moreover, the branching pair $\{\Sfr_1, \Sfr_2\}$ is
\Def{joinable} if there exists a binary tree $\Tfr'$ such that
$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$. The
diamond lemma~\cite{New42} is based upon the inspection of the branching
pairs of a terminating rewrite relation $\RewContext$ in order to prove
its confluence.
\medbreak

@@

  \item Otherwise, let $\Tfr$ be a branching tree for $\RewContext'$.
    Remove $\Tfr$ from $\BranchingTrees$.
    \smallbreak

    \item Let $\{\Sfr_1, \Sfr_2\}$ be a branching pair for $\Tfr$.
    \smallbreak

  \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms
    of $\Sfr_1$ and $\Sfr_2$, respectively.
    \smallbreak

    \item \label{item:new_rewrite_rule_buchberger}
      If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
      to $\Rew'$ the rewrite rule
    \begin{math}
        \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
        \Rew'
        \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
    \end{math}
    \smallbreak
